%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
% personal data
\name{H C}{Lalduhbera}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{24th C Cross Ejipura, Bangalore}{560047}{India}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91~8974~411~062}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{duhbera@gmail.com}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2013-2015}{Master of Technology}{Indian Institute of Technology Bombay}{Mumbai}{\textit{CPI : 8.09}}{Computer Science And Engineering}  % arguments 3 to 6 can be left empty
\cventry{2009--2013}{Bachelor of Technology}{Maulana Azad National Institute of Technology}{Bhopal}{\textit{CPI : 6.62}}{Information Technology}
\cventry{2008}{Intermediate/+2}{Mizoram Board of School Education}{Aizawl}{\textit{Percentage : 77.20}}{}
\cventry{2006}{Matriculation}{Mizoram Board of School Education}{Aizawl}{\textit{Percentage : 76.00}}{}

\section{Academic Achievements}
\begin{itemize}
    \item Scored 98.8 percentile in GATE (Graduate Aptitude Test in Engineering), Computer Science and Engineering 2013 among 2,24,160 candidates.
    \item Secured 6th rank in the HSSLC Examination 2008, conducted by the Mizoram Board of School Education.
    \begin{itemize}
    	\item 3rd highest in Mathematics and Chemistry.
    	\item 4th highest in Computer Science.
    \end{itemize}
\end{itemize}

\section{Work Experience}
\cventry{July 2015--Till Date}{Software Engineer}{HouseJoy}{Bangalore}{}{}
\begin{itemize}
	\item Designed and implemented Housejoy Subscription System.
	\item Implemented Geofencing: Used for identifying if the user's location falls in any Housejoy hubs or Housejoy Serviceable area. The implementation uses STR-tree (part of JTS Library) for indexing all Housejoy hubs which are stored as polygons for fast quering in spatial index. 
	\item Works on Redis and Spring Data Redis for caching data.
	\item Housejoy AWS IAM Administrator: Create and monitor IAM users such that each user gets access only to the appropriate AWS service and permissions. This is done by attaching IAM  policy to each user.
	\item Lead the team in designing and implementing Admin Catalogue Management System. 
	\item Modules also contributed to:
	\begin{itemize}
		\item Location Service Management System
		\item Job Management System
		\item Discount Management System
		\item Commision system
	\end{itemize}
\end{itemize}
\cvitem{Technologies/Tools}{Java, Python, Bash, SQL, Spring, Hibernate ORM, Jersey RESTful Web Services, Spring Data Redis, MySQL, Redis, Tomcat 7.x, GIT, Ant, Sequel Pro, Postman, S3cmd}

\section{Master Thesis}
\cvitem{Title}{\href{https://drive.google.com/file/d/0B1OncH_ePEbASTM5bG8ySjUycWs/view?usp=sharing}{\emph{Image based CAPTCHA  \hfill [June 2014--June 2015]}}}
\cvitem{Supervisor}{Prof. Ajit Rajwade}
\cvitem{Description}{\begin{itemize}
\item Design an Image-based CAPTCHA which can perform better than existing text-based CAPTCHA in terms of security and human usability. 
\item The CAPTCHA uses a point tracking methodology in which the user has to track a selected point from one image of a scene to another image of the same scene or object under spatial and intensity transformation.
\item Design CAPTCHA web application to study human user experience (about 150-200 users).
\item Test the strength of CAPTCHA using state of the art computer vision techniques namely, Motion Estimation and SIFT Descriptor Matching.
\end{itemize}
}
\cvitem{Technologies/Tools}{MATLAB, OpenGL, GLUT, SIFT, C++, PHP, HTML, Javascript, MySQL, ImageMagick}
\section{Key Academic Projects} 
\begin{itemize}
\item \cvitem{Title}{Constant Propagation Analysis\hfill Autumn 2013}
\cvitem{Objective}{Implement intra-procedural constant propagation analysis for Java programs. Performed byte code analysis of Java program to extract information about program flow and
variables.}
\cvitem{Technologies/Tools}{Java, Soot}
\item \cvitem{Title}{Image Splicing Detection \hfill Autumn 2013}
\cvitem{Objective}{Detection of spliced image using local noise inconsistencies. Local noise is estimated from the first-level wavelet decomposition along the diagonal sub-band HH1.}
\cvitem{Technologies/Tools}{MATLAB}
\item \cvitem{Title}{The Music Box-short 3D animated film \hfill Autumn 2013}
\cvitem{Objective}{Created a short animated film centered around a music box using OpenGL Library.}
\cvitem{Technologies/Tools}{C++, OpenGL}
\end{itemize}

\section{Technical skills}
\cvitem{Language}{C, C++, Java, Python, Bash, SQL}
\cvitem{Framework}{Spring, Hibernate ORM, Jersey RESTful Web Services, Spring Data Redis, OpenGL, GLUT}
\cvitem{Database}{MySQL, Redis}
\cvitem{Server}{Tomcat 7.x}
\cvitem{Operating System}{Mac OS X, Linux}
\cvitem{Tools}{Ant, Eclipse, Vim, MATLAB, Postman, Sequel Pro, GIT, S3cmd, ImageMagick}

%\section{Interests And Hobbies}
%\begin{itemize}
%	\item Playing and Watching football
%	\item Listening to music
%	\item Playing guitar
%\end{itemize}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\clearpage
%-----       letter       ---------------------------------------------------------
% recipient data
%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
